A holomorphic approach to membranes and fivebranes

### 2022-07-19 fivebranes/intro.tex

A principal goal of the present paper is to initiate a study of factorization algebras associated to the minimal twists of the six-dimensional $\mc N=(2,0)$ and three-dimensional $\mc N=8$ superconformal field theories. However, the six-dimensional $\cN=(2,0)$ supersymmetric theory remains quite elusive - it is non-lagrangian, and outside of the abelian case, is not known to admit a field-realization. In light of this, we propose to access the minimal twist and its local operators via \textit{twisted holography}.

@@

In section 2 we begin by recalling descriptions of minimal twists of eleven dimensional supergravity \cite{} and the abelian six-dimensional $\mc N=(2,0)$ \cite{} and three-dimensional $\mc N=8$ \cite{} superconformal field theories.

>>>>

A principal goal of the present paper is to initiate a study of factorization algebras associated to the minimal twists of the six-dimensional $\cN=(2,0)$ and three-dimensional $\cN=8$ superconformal field theories. However, the six-dimensional $\cN=(2,0)$ supersymmetric theory remains quite elusive - it is non-lagrangian, and outside of the abelian case, is not known to admit a field-realization. In light of this, we propose to access the minimal twist and its local operators via \textit{twisted holography}.

@@

In section 2 we begin by recalling descriptions of minimal twists of eleven dimensional supergravity \cite{} and the abelian six-dimensional $\cN=(2,0)$ \cite{} and three-dimensional $\cN=8$ \cite{} superconformal field theories.
